\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 europa-basics.tex
updates to arch and results mostly cosmetic

\begin{figure} \centering
  \includegraphics[scale=0.35]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/Example-NQueens1.jpg}
\caption{\small $N$-Queens solution generated by \eu}
\label{fig:nqueens-2}
\end{figure}

@@

\item \textbf{Intervals}: entities that have a temporal scope (that
  is, a beginning and an end in time) and a set of
  attributes. Intervals are used to represent actions and states in
  the planning domain.

\item \textbf{Variables and Constraints}: Variables represent Interval
  attributes and constraints enable a direct representation of
  temporal, resource and any other restrictions that a valid plan must
  comply with.

\item \textbf{Domain Configuration Rules}: This is an explicit
  representation of the conceptual relationships between actions and
  states in the problem domain, for instance, for a Shopping Agent to
  be able to purchase a product, it must be at a location where the
  product is available.

>>>>

\begin{figure}[b]
\centering
  \includegraphics[scale=0.35]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{figs/Example-NQueens1.jpg}
\caption{\small An $N$-Queens solution generated by \eu}
\label{fig:nqueens-2}
\end{figure}

@@

\begin{description}

\item[\textbf{Intervals}:] entities that have a temporal scope (that
  is, a beginning and an end in time) and a set of
  attributes. Intervals are used to represent actions and states in
  the planning domain.

\item[\textbf{Variables and Constraints}:] Variables represent Interval
  attributes and constraints enable a direct representation of
  temporal, resource and any other restrictions that a valid plan must
  comply with.

\item[\textbf{Domain Configuration Rules}:] This is an explicit
  representation of the conceptual relationships between actions and
  states in the problem domain, for instance, for a Shopping Agent to
  be able to purchase a product, it must be at a location where the
  product is available.

\end{description}
